Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-12 article.tex
Describe pilot experiment better

Would a pathogen have only peptides that do not bind to
any HLA, a pathogen would be undetected. In that case, a mutation
that causes a pathogen to become detected by a host's immune
system, may be selected against. Also, would a pathogen have only
one epitope, there would be selection for a mutation to lose it.
If there are many, say hundreds, of epitopes, the selection to lose or
gain an epitope is expected to have little effect. The relation
between the fitness of a pathogen and the number of epitopes is unknown.
One could assume a two-state fitness landscape: being
undetected, due to zero epitopes, or being detected, due to one or more
epitopes. Alternatively, one may hypothesize a gradual fitness decrease per
extra epitope.

```
[FIGURE HERE]
```

Would the pathogen have many epitopes, this study needs to 
assume a gradual fitness landscape. Due to this, we did a simple 
exploratory experiment (see 'Fitness landscape'\richel{TODO}) in which
we counted the number of epitopes in COVID-19. Because the number
of epitopes has decreased, we dared to assume a gradual fitness landscape
and to proceed with the full experiment.

@@

>>>>

Would a pathogen have only peptides that do not bind to
any HLA, a pathogen would be undetected. In that case, a mutation
that causes a pathogen to become detected by a host's immune
system, may be selected against. Also, would a pathogen have only
one epitope, there would be selection for a mutation to lose it.
If there are many, say hundreds, of epitopes, the selection to lose or
gain an epitope is expected to have little effect. The relation
between the fitness of a pathogen and the number of epitopes is unknown.
One could assume a two-state fitness landscape: being
undetected, due to zero epitopes, or being detected, due to one or more
epitopes. Alternatively, one may hypothesize a gradual fitness decrease per
extra epitope. Both fitness landscapes are depicted in 
figure \ref{fig:fitness_landscape}.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fitness_landscape.png}
  \caption{
    Two conceptual fitness landscapes. At the left is a two-state
    fitness landscape, in which the number of epitopes has a simple
    effect: a pathogen's fitness is high if it has no epitopes,
    as it is undetected by a host's immune system. 
    For one or more epitopes, fitness is at a same lower values. 
    In this fitness landscape, acquiring a second or third or more 
    epitope, this has no effect on fitness.
    At the right is a gradual fitness landscape, in which any increase in
    the number of epitopes results in a lower fitness.
  }
  \label{fig:fitness_landscape}
\end{figure}

Would the pathogen have many epitopes, this study needs to 
assume a gradual fitness landscape. Due to this, we did a simple 
exploratory experiment (see 'Fitness landscape', 
subsection \ref{subsec:fitness_landscape}) in which
we counted the number of epitopes in COVID-19. Because the number
of epitopes has decreased, we dared to assume a gradual fitness landscape
and to proceed with the full experiment.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Fitness landscape}
\label{subsec:fitness_landscape}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Reason to do before actual experiment}
This exploratory experiment tests an assumptions 
of the bigger evolutionary experiment. 
If the assumption is incorrect,
a different evolutionary experiment needs to be contrived.

\paragraph{Method in general}
For a given MHC-I haplotype, we count the number of epitopes in 
the proteome of COVID-19, at the start of the 2019 pandemic (as
described in \cite{wu2020new})
and a random strain sequenced most recently at the day of the experiment. 
Of both proteomes, we use use \verb;epitope-prediction; \cite{bianchi2017} 
to count the number of predicted binders for the HLA-A-02:01 haplotype.

\paragraph{Decision rule}
If the number of epitopes has increased, we assume a two-state fitness landscape,
in which the number of epitopes can increase neutrally by drift alone.
In this case, the experiment will be cancelled and replaced by a 
viable approach.
Else, the bigger evolutionary experiment is done as described already.
It may still be possible that the number of epitopes decreased due to drift,
but this would be a proper result in confirming the null hypothesis
of $\mathcal{H}_{3,HVB}$.

\paragraph{Method detail}
Because the proteome is only sequenced at the start of the pandemic,
we use the DNA sequences of both strains, and infer the proteome
of each, using Prodigal. Although the earlier strand has a published
proteome, we infer it regardless, as to use the same pipeline.
If needed, we tweak the Prodigal parameter settings up until
the inferred proteome of the earlier strain with known proteome
matches well enough, as concluded by eyeballing.
The parameter settings used to infer a good proteome on the earlier
strain, is then used on the genome of the more recent strain 
to infer our recent proteome.
